Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
starting to fill out background

\textbf{Dual GP}

The dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
\begin{align}
   \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - \MKzz + \vbeta_{\vu} ]^{-1} \vkzs.
\end{align}
The dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
\begin{equation} 
\begin{split}
   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \hat{\lambda}_{i}, \\
   \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{split}
\end{equation}
where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
\begin{equation}
\begin{aligned}
   \hat{\alpha}_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
   \hat{\beta}_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
\end{aligned} \label{eq:svgp_dual}
\end{equation}

>>>>

\textbf{Dual GP} Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ where $m \ll n$. The key to the complexity saving is to use a sparse distribution

dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
\begin{align}
   \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs.
\end{align}
The dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
\begin{equation} 
\begin{split}
   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \tilde{\lambda}_{i}, \\
   \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{split}
\end{equation}
where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
\begin{equation}
\begin{aligned}
   \alpha_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
   \beta_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
\end{aligned} \label{eq:svgp_dual}
\end{equation}

The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$

\textbf{Neural network to sparse GP}

\textbf{Continual learning}

\textbf{Reinforcement learning}
